---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# AssignmentB2

<!-- badges: start -->
<!-- badges: end -->

The goal of AssignmentB2 is to showcase a function I created in STAT545B. The function I created is called, `Data_overview`. This function will provide basic summary statistics of a given numerical variable y (Max-Min, Mean, and Standard Deviation), grouped by a variable x.

## Installation

AssignmentB2 is not yet on CRAN, but you can download it form this repository using the following R command: 

``` r
devtools::install.github("stat545ubc-2021/Assignments-Kaialain")
```

## Example

This is a basic example which shows you how to solve a common problem. The following example will showcase the Data_overview function using the cars dataset. Using the Data_overview function, I have retrieved the mean and standard deviation of distance travelled, grouped by the speed of the car.

```{r example}
library(AssignmentB2)

Data_overview(cars, speed, dist)
```

Currently, this is all the `Data_overview` can do. However, future developments may be added to further enhance the utility of this function.
