---
title: "Learn more about Data overview"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Learn more about Data_overview}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(AssignmentB2)
```

The `Data_overview` function will allow you to quickly examine summary statistics of a given numerical variable. However, there are some tricks you need to know to execute the function effectively.

Here is an example of how the Data_overview function works. Using the `mtcars` dataset, I will examine the variable mpg (miles per gallon) depending on the variable cyl (cylinder).

```{r}
Data_overview(mtcars, cyl, mpg)
```

It is important to note that if there are NA values in the selected numerical variable, the mean and standard deviation outputs will be NAs. The following is an example of trying to use the `Data_overview` function for variables containing NA's. 

```{r}
Data_overview(palmerpenguins::penguins, island, bill_length_mm)

```
